### 2019-01-09 Sections/costs_and_attributes_in_quantum_networks.tex
doing a second save

The \textit{mutual information} specifies the number of bits in common between two distributions. Equivalently, it is the maximum number of bits that one party can learn about the other. For two classical distributions, $A$ and $B$, this is given by,
\begin{align}\index{Mutual information}
I(A;B) = H(A) + H(B) - H(A,B).
\end{align}
Equivalently, for density operators,
\begin{align}
I(\hat\rho_A;\hat\rho_B) = S(\hat\rho_A) + S(\hat\rho_B) - S(\hat\rho_A,\hat\rho_B),
\end{align}
using the von Neuman entropy. The mutual information between two quantum states is invariant under local unitary transformations,
\begin{align}
I(\hat\rho_A;\hat\rho_B) = I(\hat{U}_A\hat\rho_A \hat{U}_A^\dag; \hat{U}_B\hat\rho_B \hat{U}_B^\dag),
\end{align}
since the eigenvalue spectrum of a density operator is invariant under unitary transformations. Therefore, the mutual information represents the maximum amount of information Bob can learn about Alice's state under \textit{any} local operations.

@@

\textbf{Mutual information}-
% 
The mutual information is defined as being between a particular known pair of states. Of course, in a quantum network we will seldom know what the states being communicated are and will therefore be unable to directly calculate the mutual information. To address this, the \textit{classical channel capacity}\index{Classical channel capacity} of a channel is defined as,
\begin{align}\index{Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \max_{\hat\rho} [I(\hat\rho,\mathcal{E}(\hat\rho))],
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

@@

\comment{Add stuff on channel capacities of different channels, like Pauli error channels etc.}

>>>>

We now introduce an entropic measure of common or mutual information that two party possesses. Suppose Alice possesses the random variable $A$ and Bob has the random variable $B$, the \textit{mutual information} specifies the number of bits in common between the two distributions. Equivalently, it is the maximum number of bits that one party can learn about the other. For two classical distributions, this is given by,
\begin{align}\index{Mutual information}
I(A;B) = H(A) + H(B) - H(A,B).
\end{align}

We can also define the classical mutual information $I_c(\rho_{AB})$ for a bipartite quantum state $\rho_{AB}$. Suppose that $\rho_{AB}$ is shared between Alice and Bob and they would like to extract maximal correlations from it. They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, which yields random varialbes $X$ and $Y$.  Their classical mutual information is given by
\begin{align}
I_c(\rho_{AB}) \equiv \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(X;Y).
\end{align}

Analogously, the quantum mutual information  for a bipartite state $\rho_{AB}$ is defined as
\begin{align}
I(A;B)_\rho = S(\hat\rho_A) + S(\hat\rho_B) - S(\rho_{AB}),
\end{align}
using the von Neuman entropy. The mutual information between two quantum states is invariant under local unitary transformations,
\begin{align}
I(A;B)_\rho = I(\hat{U}_A\hat\rho_A \hat{U}_A^\dag; \hat{U}_B\hat\rho_B \hat{U}_B^\dag),
\end{align}
since the eigenvalue spectrum of a density operator is invariant under unitary transformations. Therefore, the mutual information represents the maximum amount of information Bob can learn about Alice's state under \textit{any} local operations.

@@

% 
The mutual information is defined as being between a particular known pair of states. Of course, in a channel we have room 
play around with the input state and the measurement at the output. Therefore we can optimize the mutual information of a particular channel, which leads to the following definiiton:

The \textit{classical mutual information}\index{Classical channel capacity} of channel $\mathcal{E}$ is defined as,
\begin{align}\index{mutinfoclassical}
I(\mathcal{E}) = \max_{p(x)} I(X;Y)
% 
\end{align}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved for the channel. (Note: this definition of `capacity' is not to be confused with that which we later refer to in flow networks).

And the \textit{classical channel capacity} of $\mathcal{N}$ is defined as
\begin{align}\index{classical!Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{1}{n} \mathcal{E}^{\otimes n},
\end{align}

@@
